---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# goodpress (or badpress?)

> Write to WordPress, from R Markdown, with a modern stack.

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/maelle/goodpress/workflows/R-CMD-check/badge.svg)](https://github.com/maelle/goodpress/actions?query=workflow%3AR-CMD-check)
[![Codecov test coverage](https://codecov.io/gh/maelle/goodpress/branch/main/graph/badge.svg)](https://codecov.io/gh/maelle/goodpress?branch=main)
<!-- badges: end -->

The goal of goodpress is to post to [WordPress](https://wordpress.org/) from [R Markdown](https://rmarkdown.rstudio.com/).
I need this prototype for [a course](https://scientific-rmd-blogging.netlify.app/). 😺

**Limitation**: This package works with WordPress REST API and needs your adding an authentication plugin to your WordPress website. You can only install plugins on WordPress websites that are either **not** on wordpress.com (self-hosted; paid service somewhere) or with a costly wordpress.com business plan.

**Important disclaimer**: I don't use WordPress, so I am not sure you should trust me.
You are welcome to try out the package (not on important stuff, rather in a playground of some sort), to contribute, and to volunteer to take over this package/concept. If you write a newer and better R package please tell me about it
so I can add a link to it.

## Installation

```{r child='man/rmdhunks/installation.Rmd'} 
```

## Workflow

```{r child='man/rmdhunks/usage.Rmd'} 
```

## Motivation

```{r child='man/rmdhunks/motivation.Rmd'} 
```

